Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
half done roughing out the results section--last section to rough out!

@@

\subsubsection{Risk and Benefit Ranks} 
(REDO)

\subsubsection{Lawnmower Ratios} 
(REDO)

@@

>>>>

\subsubsection{What Matters in Upsetting People}
(REDO) Talk about the regression model here. Say that the data type was x\% responsible, the data recepient y\% responsible, and the device type z\% responsible for how upset people seemed to be when they answered the questions.

Also go into any correlations that I found with respect to demographics and the IUIPC index (I should do all of these things ASAP as soon as this paper is in good shape). There should be some interesting stuff there, whether there are specific correlations, or whether there is not. Both are good things to report and should be put here.

@@

\subsubsection{Risk and Benefit Ranks} 
(REDO) Talk through the graph shown above. The basic takeaway is that all of the new technologies and capabilities are perceived to be low risk low benefit. We can see that for technologies that people are more familiar with, people rate it more beneficial and more risky (or is it because they are more relevant that they are more familiar to them? Can I make such a claim?). Interesting to note facial recognition versus detection, location tracking, and discrete camera. Refer to appendix \ref{sec:techrank} for the details (if I have space to include such a thing as the absolute benefit and risk ranking and quartiles in this paper..).

\subsubsection{Lawnmower Ratios} 
(REDO) The basic idea for this is that I am going to compare all of the newly assessed technologies with respect to the well-studied technology generally considered to be low-risk and low-benefit, since all new technologies fit this mold. This can give a more accurate idea into how each person thought something was risky or not (twice as risky as the closest tech they know, or about equal, etc.). Do some fancy graphing stuff here. Maybe another scatter plot, or an overlay of various distributions of ratio of perceived lawnmower risk to technology risk. Hmm.

@@

\section{Risk and Benefit Rankings}
\label{sec:techrank}
